False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2016-03-16 document/ms.tex
table spacing adjusted
new validations up, some paper edits

@@

%\author{Timothy D. Morton}
%\affil{Department of Astrophysical Sciences, Princeton University}
\author{Timothy D. Morton\altaffilmark{1}, Stephen T. Bryson\altaffilmark{2}, Jeffrey L. Coughlin\altaffilmark{2,3}, Jason F. Rowe\altaffilmark{4},Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}

@@

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA, tdm@astro.princeton.edu}
\altaffiltext{2}{NASA Ames Research Center, M/S 244-30, Moffett Field, CA 94035, USA}
\altaffiltext{3}{SETI Institute, 189 Bernardo Ave, Mountain View, CA 94043, USA}
\altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}

@@

The basic idea of \vespa\ is to assign probabilities to different
astrophysical hypotheses that might describe a transiting planet
candidate signal.  If $\{H_i\}$ is the set of all considered
hypotheses, the probability for any given model $i$ is
\begin{equation}
  \eqlabel{prob}
  \mathrm{Pr}\left(H_i\right) = \frac{\pi_i \mathcal
    L_i}{\displaystyle \sum_j \pi_j \mathcal L_j},
\end{equation}
where $\pi_i$ is the ``hypothesis prior'' and $\mathcal L_i$ is the
``hypothesis likelihood''\footnote{This factor is more widely known as
  the ``Bayesian evidence'' or ``marginalized likelihood'';
  \citet{Morton:2014b} argues for the term ``hypothesis likelihood,''
  as it can be clarifying to think of it that way.}
The prior represents how intrinsically probable the hypothesized
scenario is to exist, and the likelihood represents how closely the
shape of the observed transit signal matches with the expected shape
of a signal produced by the hypothesis.

@@

@@

In order to properly interpret these results, it is necessary to
understand the range of applicability of the \vespa\ calculation.
First of all, this method selects between different \emph{eclipse
  configuration} explanations for the transit-like signal, and cannot
comment on whether the signal might be caused by stellar variability
or an instrumental false alarm.  Thus, \vespa\ results on low
signal-to-noise ratio (SNR) candidates that are not clearly
transit-like must be viewed with caution.

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/RP_cand.pdf}
\end{center}
\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
  by FPP value.  Green circles are most likely to be planets, red X's
  are most likely to be false positives, and blue plusses have
  intermediate FPPs.  Grey dots are KOIs not identified as likely 
  false positives for which the
  \vespa\ calculation is considered less reliable.  
  \figlabel{rpcand}}
\end{figure*}

>>>>

\setlength{\tabcolsep}{2pt}

@@

%\author{Timothy D. Morton}
%\affil{Department of Astrophysical Sciences, Princeton University}
\author{Timothy D. Morton\altaffilmark{1}, Stephen T. Bryson\altaffilmark{2}, Jeffrey L. Coughlin\altaffilmark{2,3}, Jason F. Rowe\altaffilmark{4}, Ganesh Ravichandran\altaffilmark{5}, Erik A. Petigura\altaffilmark{6}, 
Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}

@@

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA, tdm@astro.princeton.edu}
\altaffiltext{2}{NASA Ames Research Center, M/S 244-30, Moffett Field, CA 94035, USA}
\altaffiltext{3}{SETI Institute, 189 Bernardo Ave, Mountain View, CA 94043, USA}
\altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
\altaffiltext{5}{Columbia University}
\altaffiltext{6}{California Institute of Technology}

@@

The basic idea of \vespa\ is to assign probabilities to different
hypotheses that might describe a transiting planet
candidate signal.  If $\{H_i\}$ is the set of all considered
hypotheses, the probability for any given model $i$ is
\begin{equation}
  \eqlabel{prob}
  \mathrm{Pr}\left(H_i\right) = \frac{\pi_i \mathcal
    L_i}{\displaystyle \sum_j \pi_j \mathcal L_j},
\end{equation}
where $\pi_i$ is the ``hypothesis prior'' and $\mathcal L_i$ is the
``hypothesis likelihood''\footnote{This factor is more widely known as
  the ``Bayesian evidence'' or ``marginalized likelihood'';
  \citet{Morton:2014b} argues for the term ``hypothesis likelihood,''
  as it can be clarifying to think of it that way.}
The prior represents how intrinsically probable the hypothesized
scenario is to exist, and the likelihood represents how closely the
shape of the observed transit signal matches with the expected shape
of a signal produced by the hypothesis.

@@

We note that a built-in weakness of model selection is that it assumes that
the set of models being considered is comprehensive.  This could
in principle lead to a situation where one model is strongly preferred
over all other models, but even that model is a poor explanation of
the data---in this work, this could lead to improperly validated planets.  
There are two general strategies to try to address this issue.  The first 
is to somehow quantify the absolute goodness-of-fit of the models, and 
require that a validated planet pass some threshold test.  The other 
strategy, that we adopt here, is to expand the set of models to be more 
comprehensive.  In order to do this, we introduce two artificial models:
``boxy'' and ``long.''  The ``boxy'' likelihood function is a step function
at some minimum value of $T/\tau$ (zero below this threshold, and constant
above), and constant throughout the space of the other trapezoidal parameters.
Similarly, the likelihood of the ``long'' model is a step function at some
minimum threshold value of duration $T$.  These thresholds  
are set relative to the simulated trapezoidal shapes of the planet model:
the $T/\tau$ threshold is the maximum value from the simulated planet population,
and the $T$ threshold is the 99\% percentile of simulated planet
population values.  We also choose the model priors for these artificial
models to be low, reflecting that we expect only a small number of signals
to be unexplained by any of the astrophysical scenarios: the number that we
choose for each of these models is $5 \times 10^{-5}$, corresponding to an expectation
that there may be $\sim$10 such signals among the $\sim$200,000 \kepler\ targets.

@@

In order to properly interpret these results, it is necessary to
understand the range of applicability of the \vespa\ calculation.
First of all, this method selects between different specific explanations 
for the transit-like signal, and cannot
comment on whether the signal might be caused by stellar variability
or an instrumental false alarm.  Thus, \vespa\ results on low
signal-to-noise ratio (SNR) candidates that are not clearly
transit-like must be viewed with caution.  This being said, the reason 
for including the artificial 
``boxy'' and ``long'' models in the model selection calculation
 (\sect{mothods:fpp}) is to flag signals that do not 
fit well with any of the astrophysical eclipse models---and despite their
contrived nature, they do seem to

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fppalpha.pdf}
\end{center}
\caption{Periods and radii of KOIs with CANDIDATE and CONFIRMED disposition.  
  Blue circles have previously been identified as CONFIRMED.  Candidates are orange circles, 
  shaded by false positive probability, with 
  a transparent circle representing a high FPP. 
  \figlabel{rpcand}}
\end{figure*}
